### 2015-03-24 src/paper3/p3_discussion.tex
Updated paper 3

We investigated the contribution of eye movements to the perception of passively-induced self-motion. Experiments were performed in the absence of full-field optic flow to eliminate the contribution of this visual motion signal. Perception of self-motion was compared across three fixation types: during free fixation the fixation target was extinguished before the movement, while during world and body fixation, targets  remained stable relative to the world and body, respectively. Our results show that self-motion is underestimated during body fixation (in which the eyes remain stationary) compared to world fixation (in which the eyes move to maintain fixation).The eye movements during free fixation, which  are driven by the VOR, show a non-unity gain with excursions in-between body- and world-fixation conditions. Self-motion perception reflects this pattern of eye movements, suggesting an important contribution of this extraretinal signal to to the perception of self-motion.

 To quantitatively characterize the separate vestibular and eye movement contributions, we fitted a single parameter model to the perceptual responses for the body versus world comparison conditions and validated this model independently by predicting the effects of eye movements on self-motion perception during free fixation conditions. This model takes into account subject specific oculomotor weight and eye movement patterns. Based on these inputs it accurately predicts the responses in the free fixation conditions. This demonstrates that extra-retinal eye movement signals are used as a cue in the perception of self-motion, contributing significantly to the self-motion percept with a weight of approximately 25 percent, even in the absence of optic flow.

@@

In the above, we suggest that eye movements themselves drive perception of self-motion. However, it is conceivable that a common correlate of eye movements, such as attention or visual motion influenced our results. In 1963, Guedry and Harris reported a substantial underestimation of displacement when their observers watched a small body-fixed target compared to displacements in the dark. They attributed their findings to an attentional shift from judgments of body displacement in the dark to judgments of target displacement in the fixation condition. We favor an explanation by eye movements.  In their study, it is likely that the VOR caused eye movements  to occur during the translations in darkness. If these movements were used to augment self-motion perception, then the perception of such translations would be overestimated compared to translations made without eye movements, e.g. when fixating a body-fixed target. Because Guedry and Harris \citeyear{guedry1963} did neither record nor explicitly manipulate eye movements, they were not able to unveil their explicit role. Likewise, we did not manipulate attentional processes \cite{kitazaki2003}, so we cannot completely exclude the possibility they play a role.

>>>>

We investigated the contribution of eye movements to the perception of passively-induced self-motion. Experiments were performed in the absence of full-field optic flow to eliminate the contribution of this visual motion signal. Perception of self-motion was compared across three fixation types: during free fixation the fixation target was extinguished before the movement, while during world and body fixation, targets  remained stable relative to the world and body, respectively. Our results show that self-motion is underestimated during body fixation (in which the eyes remain stationary) compared to world fixation (in which the eyes move to maintain fixation).The eye movements during free fixation, which  are driven by the VOR, show a non-unity gain with excursions in-between body- and world-fixation conditions. Self-motion perception reflects this pattern of eye movements, suggesting an important contribution of this extraretinal signal to the perception of self-motion.

 To quantitatively characterize the separate vestibular and eye movement contributions, we fit a single parameter model to the perceptual responses for the body versus world comparison conditions and validated this model independently by predicting the effects of eye movements on self-motion perception during free fixation conditions. This model takes into account subject specific oculomotor weight and eye movement patterns. Based on these inputs it accurately predicts the responses in the free fixation conditions. This demonstrates that extra-retinal eye movement signals are used as a cue in the perception of self-motion, contributing significantly to the self-motion percept with a weight of approximately 25 percent, even in the absence of optic flow.

@@

In the above, we suggest that eye movements themselves drive perception of self-motion. However, it is conceivable that a common correlate of eye movements, such as attention or visual motion influenced our results. In 1963, Guedry and Harris reported a substantial underestimation of displacement when their observers watched a small body-fixed target compared to displacements in the dark. They attributed their findings to an attentional shift from judgements of body displacement in the dark to judgements of target displacement in the fixation condition. We favor an explanation based on eye movement characteristics.  In their study, it is likely that the VOR caused eye movements  to occur during the translations in darkness. If these movements were used to augment self-motion perception, then the perception of such translations would be overestimated compared to translations made without eye movements, e.g. when fixating a body-fixed target. Because Guedry and Harris \citeyear{guedry1963} did neither record nor explicitly manipulate eye movements, they were not able to unveil their explicit role. Conversely, we did not manipulate attentional processes \cite{kitazaki2003}, so we cannot completely exclude the possibility they play a role.

### 2015-03-24 src/paper3/p3_intro.tex
Updated paper 3

An accurate estimate of self-motion is important to guide interactions with the environment. During passive self-motion both vestibular and optic flow signals provide information about self-motion \cite{gibson1955, benson1986, harris2000, israel1989, angelaki2005, carriot2013, chen2010}. However, also compensatory eye movements that maintain fixation on world-fixed objects carry self-motion information. These eye movements are driven by retinal slip or vestibular signals. For example, the linear vestibulo-ocular reflex (LVOR) stabilizes gaze during head translations, even in complete darkness \cite{paige1989,medendorp2002,angelaki2004}.  Many have shown that the brain uses oculomotor signals to extract the optic flow component related to self-motion \cite{warren1988, royden1992, freeman1998, lappe1999}, but to our knowledge a possible direct influence of eye movements on self-motion perception has not been investigated. Here we investigate whether these oculomotor signals are also used to estimate self-motion directly.

>>>>

An accurate estimate of self-motion is important to guide interactions with the environment. During passive self-motion both vestibular and optic flow signals provide information about self-motion \cite{gibson1955, benson1986, harris2000, israel1989, angelaki2005, carriot2013, chen2010}. However, also compensatory eye movements that maintain fixation on world-fixed objects carry self-motion information. These eye movements are driven by retinal slip or vestibular signals. For example, the linear vestibulo-ocular reflex (LVOR) stabilizes gaze during head translations, even in complete darkness \cite{paige1989,medendorp2002,angelaki2004}.  Many studies have shown that the brain uses oculomotor signals to extract the optic flow component related to self-motion \cite{warren1988, royden1992, freeman1998, lappe1999}, but to our knowledge a direct influence of eye movements on self-motion perception has not been investigated. Here we study whether these oculomotor signals are also used to estimate self-motion directly.

### 2015-03-24 src/paper3/p3_methods.tex
Updated paper 3

A motorized linear sled \cite<see>[for details]{clemens2012} was used to laterally translate participants following a minimum jerk profile \cite{flash1985} of fixed duration (1 \si{\second}) and amplitudes ranging from 1 to 27 \si{\centi\metre}. Participants were seated on the sled such that the inter-aural axis aligned with the motion axis. They were restrained using a five-point seat belt and a chin rest. In addition, the head was held in place using a sled-fixed mold which resembled head-phones and pressed down on the head surrounding the pinnea . Auditory cues were suppressed using white noise presented through in-ear headphones. Experiments were conducted in complete darkness except for visual fixation points, projected by a laser pointer on a black bar 50 \si{\centi\metre} in front of the participant at eye level. Laser pointers used to project body-fixed targets were attached to the sled. Those used to project world-fixed targets were mounted on the wall behind the sled.

Eye movements were recorded at 500\si{\hertz} using an EyeLink II (SR Research, Kanata, Canada) system whose cameras were mounted to the sled and therefore remained stable with respect to the head during the entire experiment. Because the head and body positions were fixed during the experiment, the orientation of the eyes within the head, as measured by the tracker, was equivalent to the orientation of the eyes in space. The eye tracking system was calibrated before each session using 11 evenly spaced calibration points ranging from -22 to \siang{22} degrees. We used linear regression to link EyeLink measurements to gaze angles.

@@

Thus, a trial consists of two translations with different fixation types; in the three main conditions we compare the body versus world, world versus free, and body versus free fixation types. For each main condition, we varied which fixation type served as the reference stimulus and the order in which reference and probe were presented, which gives a total of four variations per main condition (see \tabref{p3:tab1}). In addition we varied translation direction (either leftward or rightward on consecutive trials). The amplitude of the probe translation was adaptively chosen using the Psi method. This method picks the amplitude for the next trial which maximizes the expected decrease in entropy based on participants’ responses to earlier trials \cite{kontsevich1999}. This was done separately for all 24 trial types (3 main conditions x 2 reference stimuli x 2 reference/probe orders x 2 translation directions; see \tabref{p3:tab1}). A total of 25 trials were collected per trial type yielding a total of 200 trials for each of the three main conditions.

Trials were presented in three one-hour sessions. To prevent dark adaptation, we turned on the lights for 5 \si{\second} after every block of 6 trials, and for at least 30 seconds every 4 blocks. We made sure that each of the 24 unique trial types were presented once every 4 blocks. After each block, the adaptive procedure determined which translation amplitudes to test in the following block. To increase the number of data-points available to the adaptive psychometric procedure at the beginning of the experiment, we collapsed across translation direction and reference order for the first 10 trials of every condition. After those collapsed trials, the procedure ran separately for each of the 24 distinct trial types.

@@

For each trial type (see \tabref{p3:tab1}), we also qualified eye movements, corrected for drift, based on initial fixation. The main source of drift were tiny lateral movements of the eye tracking cameras due to sled motion. We discarded trials containing blinks as well as trials in which the final eye position exceeded two standard deviations from the condition's average. Based on these criteria, 6.1\%, 3.6\% and 1.6\% of all trials were rejected based on errors in body, world, and free fixation respectively. In addition we rejected 1.2\% of all trials because participants blinked within the movement interval.

For the remaining trials, we computed the average ratio between the measured eye excursion, $\varphi_i$, and the angle that woud be needed were the trial testing the world-fixed condition. The latter is computed by taking the arc-tangent of the actual translation distance, $m_i$, divided by the fixation depth, $d_i$, which for small $\varphi$ can be approximated by $g = \varphi m/d$. We computed this ratio, $g$, for every fixation type and interval (see \tabref{p3:tab1}). Ideally, for body-fixed trials $g = 0$, and for world-fixed trials $g = 1$. Using this ratio, we are able to compute the expected eye excursion, $\hat{\varphi} = gd/m$, for any given translation distance even those we did not explicitly measure.

\subsubsection{Model}

Using a simple cue integration model, we investigated whether inter-subject and inter-condition differences in the observed PSEs in conditions containing a translation under free fixation depend on actual eye movement behavior. We modeled perceived distance, $p$, as a weighted linear combination of a vestibular and an oculomotor estimate of translation (\eqnref{p3:eq2}). We assumed that the vestibular estimate is equal to the actual translation, $m$, and that the oculomotor estimate is equal to expected eye movement given the  actual, $\hat{\varphi}_{m_i}$. As the weights represent the relative contributions of the oculomotor and vestibular systems, they can sum to any arbitrary value; in \eqnref{p3:eq2} they are fixed to 1. Thus, the weighting parameter $\alpha$ regulates the eye movement contribution and $1 - \alpha$  the vestibular contribution:

@@

By only using data from conditions where a visual fixation point was present (i.e. body versus world) to fit the model, we examined if the same weight $\alpha$ also explains the PSEs found in the conditions where fixation was free. To this end, we solved Equation 3 for $m_p$ and computed PSE estimates, $P\hat{S}E$, for the body versus free and world versus free conditions (\eqnref{p3:eq5}).
                                                                                            \begin{equation}
\label{p3:eq5}
\hat{m}_p = P\hat{S}E = \frac
	{\alpha g_r + (1 - \alpha)}
	{\alpha g_p + (1 - \alpha)}
    m_r
\end{equation}

In addition to minimizing the sum of squared errors in \eqnref{p3:eq4}, we also fit \eqnref{p3:eq5} to the data in order to see if weight α depends on the way the model is formulated. Parameters obtained by fitting \eqnref{p3:eq5} fell well within the standard deviation reported in \tabref{p3:tab2} for all participants, suggesting that they did not depend on the way the model was formulated.

>>>>

A motorized linear sled \cite<see>[for details]{clemens2012} was used to laterally translate participants following a minimum jerk profile \cite{flash1985} of fixed duration (1 \si{\second}) and amplitudes ranging from 1 to 27 \si{\centi\metre}. Participants were seated on the sled such that the inter-aural axis aligned with the motion axis. They were restrained using a five-point seat belt and a chin rest. In addition, the head was held in place using a sled-fixed mold which resembled head-phones and pressed down on the head surrounding the pinnae. Auditory cues were suppressed using white noise presented through in-ear headphones. Experiments were conducted in complete darkness except for visual fixation points, projected by a laser pointer on a black bar 50 \si{\centi\metre} in front of the participant at eye level. Laser pointers used to project body-fixed targets were attached to the sled. Those used to project world-fixed targets were mounted on the wall behind the sled.

Eye movements were recorded at 500\si{\hertz} using an EyeLink II system (SR Research, Kanata, Canada) whose cameras were mounted to the sled and therefore remained stable with respect to the head during the entire experiment. Because the head and body positions were fixed during the experiment, the orientation of the eyes within the head, as measured by the tracker, was equivalent to the orientation of the eyes in space. The eye tracking system was calibrated before each session using 11 evenly spaced calibration points ranging from -22 to \siang{22} degrees. We used linear regression to link EyeLink measurements to gaze angles.

@@

Thus, a trial consists of two translations with different fixation types; in the three main conditions we compare the body versus world, world versus free, and body versus free fixation types. For each main condition, we varied which fixation type served as the reference stimulus and the order in which reference and probe were presented, which gives a total of four variations per main condition (see \tabref{p3:tab1}). In addition we varied translation direction (either leftward or rightward on consecutive trials). The amplitude of the probe translation was adaptively chosen using the Psi method. This method picks the amplitude for the next trial which maximizes the expected decrease in entropy based on participants' responses to earlier trials \cite{kontsevich1999}. This was done separately for all 24 trial types (3 main conditions x 2 reference stimuli x 2 reference/probe orders x 2 translation directions; see \tabref{p3:tab1}). A total of 25 trials were collected per trial type yielding a total of 200 trials for each of the three main conditions.

Trials were presented in three one-hour sessions. To prevent dark adaptation, we turned on the lights for 5 \si{\second} after every block of 6 trials, and for at least 30 \si{\second} every 4 blocks. We made sure that each of the 24 unique trial types were presented once every 4 blocks. After each block, the adaptive procedure determined which translation amplitudes to test in the following block. To increase the number of data-points available to the adaptive psychometric procedure at the beginning of the experiment, we collapsed across translation direction and reference order for the first 10 trials of every condition. After those collapsed trials, the procedure ran separately for each of the 24 distinct trial types.

@@

For each trial type (see \tabref{p3:tab1}), we also quantified eye movements, corrected for drift, based on initial fixation. The main source of drift were tiny lateral movements of the eye tracking cameras due to sled motion. We discarded trials containing blinks as well as trials in which the final eye position exceeded two standard deviations from the condition's average. Based on these criteria, 6.1\%, 3.6\% and 1.6\% of all trials were rejected based on errors in body, world, and free fixation respectively. In addition we rejected 1.2\% of all trials because participants blinked within the movement interval.

For the remaining trials, we computed the average ratio between the measured eye excursion, $\varphi_i$, and the angle that would be needed were the trial testing the world-fixed condition. The latter is computed by taking the arc-tangent of the actual translation distance, $m_i$, divided by the fixation depth, $d_i$, which for small $\varphi$ can be approximated by $g = \varphi m/d$. We computed this ratio, $g$, for every fixation type and interval (see \tabref{p3:tab1}). Ideally, for body-fixed trials $g = 0$, and for world-fixed trials $g = 1$. Using this ratio, we are able to compute the expected eye excursion, $\hat{\varphi} = gd/m$, for any given translation distance even those we did not explicitly measure.

\subsubsection{Model}
\label{p3:sec:model}

Using a simple cue integration model, we investigated whether inter-subject and inter-condition differences in the observed PSEs in conditions containing a translation under free fixation depend on actual eye movement behavior. We modeled perceived distance, $p$, as a weighted linear combination of a vestibular and an oculomotor estimate of translation (\eqnref{p3:eq2}). We assumed that the vestibular estimate is equal to the actual translation, $m$, and that the oculomotor estimate is equal to expected eye movement given the  actual, $\hat{\varphi}_{m_i}$. As the weights represent the relative contributions of the oculomotor and vestibular systems, they can sum to any arbitrary value; in \eqnref{p3:eq2} their sum is fixed to 1. Thus, the weighting parameter $\alpha$ regulates the eye movement contribution and $1 - \alpha$  the vestibular contribution:

@@

By only using data from conditions where a visual fixation point was present during both translations (i.e. body versus world) to fit the model, we could examine whether the same weight $\alpha$ can also explain the PSEs found in the conditions containing a free fixation interval. To this end, we solved Equation 3 for $m_p$ and computed PSE estimates, $P\hat{S}E$, for the body versus free and world versus free conditions (\eqnref{p3:eq5}).
                                                                                            \begin{equation}
\label{p3:eq5}
\hat{m}_p = P\hat{S}E = \frac
	{\alpha g_r + (1 - \alpha)}
	{\alpha g_p + (1 - \alpha)}
    m_r
\end{equation}

In addition to minimizing the sum of squared errors in \eqnref{p3:eq4}, we also fit \eqnref{p3:eq5} to the data in order to see if weight $\alpha$ depends on the way the model is formulated. Parameters obtained by fitting \eqnref{p3:eq5} fell well within the standard deviation reported in \tabref{p3:tab2} for all participants, suggesting that they did not depend on the way the model was formulated.

### 2015-03-24 src/paper3/p3_results.tex
Updated paper 3

The performance of one participant is illustrated in the left column of \figref{p3:fig2}. Each row shows one main condition: body versus world fixation (top/red), world versus free fixation (middle/green), and body versus free fixation (bottom/blue). The lighter and darker colors in each panel indicate which fixation type was the reference movement (see Legend). The shift of the psychometric functions relative to the 10 \si{\centi\metre} reference (i.e. the PSE) quantifies the influence of fixation type. For example, the rightward shift of the light red curve in \figref{p3:fig2}A means that for a body fixation a longer translation (\about 19 \si{\centi\metre}) was required for that translation to be perceived equivalent to a 10\si{\centi\metre} reference translation with world fixation. On the other hand, the leftward shift of the dark red curve means that a shorter translation with world fixation (\about 7 \si{\centi\metre}) was required for that translation to be perceived equivalent to the 10 \si{\centi\metre} reference translation with body fixation. Together, these oppositely directed shifts demonstrate that translations with world fixation were perceived longer than equivalent translations with body fixation, regardless of which translation was the reference.  Similarly, the shifts in \figref{p3:fig2}B shows that world fixation translations were also perceived to be longer than free fixation movements and \figref{p3:fig2}C shows that free fixation translations were perceived to be longer than body fixation translations. Note that Figure 2 also shows an effects on slope, which will be further discussed in the paragraph \nameref{p3:sec:precision}.

Similar results were obtained for all subjects, as shown by the individual PSEs for all participants (right column of \figref{p3:fig2}). Statistical significance of the fixation-induced effects for each main condition (world versus body, \figref{p3:fig2}D; world versus free, \figref{p3:fig2}E; and free versus body, \figref{p3:fig2}F) was evaluated by comparing PSEs between the two reference conditions using a paired t-test. These PSEs were significantly different in all cases (world versus body, \ttest{7}{-4.09}{0.05}; world versus free, \ttest{7}{-2.48}{0.05}; free versus body, \ttest{7}{-3.38}{0.05}. As for the example subject, these results indicate that translations made with body fixation are perceived shorter than with world fixation, suggesting that self-motion perception is modulated by eye movements even in absence of full-field optic flow. The free fixation translations, which controlling for confounds of the small the fixation point, were perceived to be longer than body and shorter than world fixation translation intervals, which could be expected if their gain would be smaller than 1 but larger than 0.

@@

To quantify the role of eye movements in self-motion, we tested a linear model in which perceived translation is a weighted average of a vestibular estimate (equal to the actual translation) and an oculomotor estimate (equal to the normalized eye movement times the actual translation; \eqnref{p3:eq2}). This model contains a single free parameter ($\alpha$), which corresponds to the relative weight given to the oculomotor estimate. We fitted this model to the two body versus world conditions and obtained the value of the oculomotor weight for every subject (\tabref{p3:tab2}). The average oculomotor weight is 0.25 \textpm0.12 (SD), indicating that the contribution of the eye movement signal to the self-motion estimate is about 25 percent. Note that participant 4, whose oculomotor weight is furthest from this mean ($\alpha = 0.06$), also shows a radically different eye movement gain during the free-fixation (see \figref{p3:fig3}B). We then used these oculomotor weights along with the normalized eye movement values to predict the PSEs in the remaining four conditions according to \eqnref{p3:eq5}. The predicted PSEs are plotted against the actually observed PSEs in \figref{p3:fig4}. The positive correlation ($\rho = 0.78$, $p < 0.01$) between observed and predicted PSEs suggests that eye movements are indeed used in self-motion perception, even in the absence of a fixation point (i.e. during free fixation). Furthermore, the fact that data points generally cluster near the unity line shows that our simple model does reasonably well in predicting perceptual performance across subjects and conditions based on oculomotor weight and normalized eye movement magnitude only. This holds true even for subject 7 whose oculomotor weight (\tabref{p3:tab2}) was approximately double the average, yet whose data points remain close to the unity line.

@@

\subsection{Precision depends on the PSE}
\label{p3:sec:precision}

The psychometric curves of the example participant in \figref{p3:fig2} show that precision ($\sigma^{-2}$ in \eqnref{p3:eq1}) decreases as the difference between translated distance in the reference and probe intervals (i.e. the bias) increases. To further investigate this effect, \figref{p3:fig5} shows a linear relation ($R^2 = 0.64$) between the bias and precision across all participants and conditions. This effect, which follows Weber’s perceptual law \cite{fechner1860} is consistent with the signal-dependence of (discrimination) precision that has been shown recently for vertical self-motion \cite{nesti2014}.

>>>>

The performance of one participant is illustrated in the left column of \figref{p3:fig2}. Each row shows one main condition: body versus world fixation (top/red), world versus free fixation (middle/green), and body versus free fixation (bottom/blue). The lighter and darker colors in each panel indicate which fixation type was the reference movement (see Legend). The shift of the psychometric functions relative to the 10 \si{\centi\metre} reference (i.e. the PSE) quantifies the influence of fixation type. For example, the rightward shift of the light red curve in \figref{p3:fig2}A means that for a body fixation a longer translation (\about 19 \si{\centi\metre}) was required for that translation to be perceived equivalent to a 10\si{\centi\metre} reference translation with world fixation. On the other hand, the leftward shift of the dark red curve means that a shorter translation with world fixation (\about 7 \si{\centi\metre}) was required for that translation to be perceived equivalent to the 10 \si{\centi\metre} reference translation with body fixation. Together, these oppositely directed shifts demonstrate that translations with world fixation were perceived longer than equivalent translations with body fixation, regardless of which translation was the reference.  Similarly, the shifts in \figref{p3:fig2}B shows that world fixation translations were also perceived to be longer than free fixation movements and \figref{p3:fig2}C shows that free fixation translations were perceived to be longer than body fixation translations. Note that \figref{p3:fig2} also shows effects on slope, which will be further discussed in the paragraph \nameref{p3:sec:precision}.

Similar results were obtained for all subjects, as shown by the individual PSEs for all participants (right column of \figref{p3:fig2}). Statistical significance of the fixation-induced effects for each main condition (world versus body, \figref{p3:fig2}D; world versus free, \figref{p3:fig2}E; and free versus body, \figref{p3:fig2}F) was evaluated by comparing PSEs between the two reference conditions using a paired t-test. These PSEs were significantly different in all cases (world versus body, \ttest{7}{-4.09}{0.05}; world versus free, \ttest{7}{-2.48}{0.05}; free versus body, \ttest{7}{-3.38}{0.05}. As for the example subject, these results indicate that translations made with body fixation are perceived shorter than with world fixation, suggesting that self-motion perception is modulated by eye movements even in absence of full-field optic flow. The free fixation translations, which control for confounds of the small fixation point, were perceived to be longer than body and shorter than world fixation translation intervals, which could be expected if their gains were smaller than 1 but larger than 0.

@@

To quantify the role of eye movements in self-motion perception, we tested a linear model (see \nameref{p3:sec:model}) in which perceived translation is a weighted average of a vestibular estimate (equal to the actual translation) and an oculomotor estimate (equal to the normalized eye movement times the actual translation; \eqnref{p3:eq2}). This model contains a single free parameter ($\alpha$), which corresponds to the relative weight given to the oculomotor estimate. We fit this model to the two body versus world conditions and obtained the value of the oculomotor weight for every subject (\tabref{p3:tab2}). The average oculomotor weight is 0.25 \textpm0.12 (SD), indicating that the contribution of the eye movement signal to the self-motion estimate is about 25 percent. Note that participant 4, whose oculomotor weight is furthest from this mean ($\alpha = 0.06$), also shows a radically different eye movement gain during the free-fixation (see \figref{p3:fig3}B). We then used these oculomotor weights along with the normalized eye movement values to predict the PSEs in the remaining four conditions according to \eqnref{p3:eq5}. The predicted PSEs are plotted against the actually observed PSEs in \figref{p3:fig4}. The positive correlation ($\rho = 0.78$, $p < 0.01$) between observed and predicted PSEs suggests that eye movements are indeed used in self-motion perception, even in the absence of a fixation point (i.e. during free fixation). Furthermore, the fact that data points generally cluster near the unity line shows that our simple model does reasonably well in predicting perceptual performance across subjects and conditions based on oculomotor weight and normalized eye movement magnitude only. This holds true even for subject 7 whose oculomotor weight (\tabref{p3:tab2}) was approximately double the average, yet whose data points remain close to the unity line.

@@

\subsection{Precision depends on PSE}
\label{p3:sec:precision}

The psychometric curves of the example participant in \figref{p3:fig2} show that precision ($\sigma^{-2}$ in \eqnref{p3:eq1}) decreases as the difference between translated distance in the reference and probe intervals (i.e. the bias) increases. In \figref{p3:fig5} precision is plotted as a functions of bias for all participants and all conditions, showing a significant linear relationship ($R^2 = 0.64$) between the two. This effect, which follows Weber's perceptual law \cite{fechner1860} is consistent with the signal-dependence of (discrimination) precision that has been shown recently for vertical self-motion \cite{nesti2014}.
